R tools for accessing research literature for text mining

### 2019-08-23 manuscript.Rmd
intro change

The R programming language is used widely throughout many academic fields;
tools in R for text mining are of particular importance because they
can be adopted by academics rapidly.

>>>>

The R programming language is free of cost, and is used widely throughout
many academic fields; tools in R for text mining are of particular
importance because they can be adopted by academics rapidly.
